A catalog of wide binaries and comoving star pairs from \textsl{Gaia DR1} and low-resolution spectroscopy

### 2017-07-05 paper/comoving-followup.tex
second cmd

\subsection{Physical properties of genuine comoving pairs}\label{sec:separation}

@@

@@

\subsection{Galactic orbits of the co-moving pairs}\label{sec:}

\todo{Orbits of true pairs in the Galaxy, any halo or thick-disk?}

>>>>

\subsection{Properties of genuine comoving pairs}\label{sec:genuine}

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{genuine_cmd.pdf}
  \end{center}
  \caption{%
    Color-magnitude diagram of \emph{genuine} comoving star pairs plotted over
    the density of all \tgas\ sources within 200 pc; similar to
    \figurename~\ref{fig:sample-cmd}, but for only the genuine comoving
    pairs.
    Several interesting pairs that include main-sequence and giant component
    stars are highlighted in the text
    (\sectionname~\ref{sec:interesting-pairs}).
    \label{fig:genuine-cmd}}
\end{figure}

@@

\subsection{Interesting comoving pairs}\label{sec:interesting-pairs}

\todo{Highlight the MS-Giant pairs}
\todo{Highlight the binary sequence-main sequence pairs}
